Matching Bullets

### 2015-12-03 imaging-paper.Rnw
Test the get peaks function

my.loess$fitted
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_resid} Residuals of Loess fit for land 1 of bullet 1.}
<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE>>=
my.loess <- fit_loess(br111_bullet, br111.groove)

my.loess$resid
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to land 1 of bullet 1 (Barrel 1).}
\end{figure}

>>>>

my.loess$fitted
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_resid} Residuals of Loess fit for land 1 of bullet 1.}
<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE>>=
my.loess$resid
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to land 1 of bullet 1 (Barrel 1).}
\end{figure}
